\textbf{BERTmoji} says: "wear a mask" : \includegraphics[scale=0.07]{images/mask_photo.png}

### 2020-08-27 paper/main.tex
commit_main-tex

\begin{figure}
    \centering
    \includegraphics[height=2in]{images/dis_country.eps}
    \caption{The spatial distribution of the $\emoticon$ dataset.}
    \label{fig:corona:spatial}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[height=2in]{images/dis_lang.eps}
    \caption{The language distribution of the $\emoticon$ dataset.} 
    \label{table:lang}
\end{figure}

@@

%\begin{figure}%
%    \centering
%    \subfloat{{\includegraphics[scale=0.78]{images/emojitable.pdf}}}%
%    \label{adsad}
%    \subfloat{{\includegraphics[scale =0.21]{emoticonwheel.jpg} }}%
%    \caption{2 Figures side by side}%
%    \label{fig:example}%
%\end{figure}

@@

Importantly, duplicate tweets are included in the $\corona$ dataset,
but they are not included in the $\emoticon$ dataset.
This is because of the purpose of the $\emoticon$ dataset. 
We aimed to apply our $\model$ to this dataset,
which is something with free user input where our training data is not fully representative of the eventual data our model will be applied to.
Therefore this limits our abilities to make assumptions and could possibly inflate our sense of model efficacy.
On the other hand when dealing with the $\corona$ dataset,
duplicate inputs result in some distribution on our outputs.
Since we want to map out the public's emotional response to the coronavirus, it is important 
for those distributions to be maintained.
\fixme{Can you come up with an explanation about why this is good or bad?}

@@

\subsection{Training procedure and performance on $\emoticon$}
To generate $\model$, we utilized the pre-trained BERT model \cite{bert} by fine-tuning it to our multilingual emoji prediction task. 
BERT is a new language representation model, which is aimed in pretraining deep bidirectional representations from unlabeled text by jointly conditioning on both left and right context in all layers.
Therefore, the pre-trained model can be easily fine-tuned by adding another output layer.
One of the reasons why we picked BERT is due to its performance on the General Language Understanding Evaluation (GLUE) \cite{} benchmark.
It is comprised of nine language understanding tasks, assembled from a diverse dataset which includes insight into model performance with respect to a wide range of linguistic phenomena.
At the time of writing, BERT and its variations hold a number of top achieving scores in the GLUE leaderboard \ref{leaderboard}.

@@

\begin{figure}[ht]
    \centering
    \fixme{image not included in repo.}
    %\includegraphics[width=\textwidth]{images/TOP15EMOJIPERF.pdf}
    \caption{F1-score performance on the top 15 performing emojis out of the 80 emojis trained. 
    \textbf{BERTmoji L.L} is the model where the last layer is trained. \textbf{BERTmoji} is the fully trained model.}
    \label{fig:tweets_per_day}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \fixme{image not included in repo.}
    %\includegraphics[width=\textwidth]{images/TOP15LANGPERF.pdf}
    \caption{F1-score performance on the top 15 languages in the $\emoticon$ based on the number of tweets for each language.
    \textbf{BERTmoji L.L} is the model where the last layer is trained. \textbf{BERTmoji} is the fully trained model.}
    \label{fig:tweets_per_day}
\end{figure}
We now precede in testing \textbf{BERTmoji} ability to predict emojis for different languages.
We decided on picking an English sentence that expressed emotions and could possibly appear in twitter,
we then translated from English to the other nine languages from Figure 2 using Google Translate.
The sentence was: "Thinking about all the things I didn't do today, ok bed time ... \#tired \#sleep."
In addition, we also applied the sliding window algorithm to the translated sentences,
in order to observe which words were more significant for the \textbf{BERTmoji} across the translations.
The results are shown in Figure 6.

\begin{figure}[ht]
    \centering
    \fixme{image not included in repo.}
    %\includegraphics[width=\textwidth]{images/PREDICTMOJI.pdf}
    \caption{The table first column presents the top 10 languages of our $\emoticon$; 
    the second column includes the sliding window interpretations of the translations from the original English sentence performed with Google Translate;
    the third column shows the resulting top 5 emojis \textbf{BERTmoji} generated.
     }
    \label{fig:prediction_top10_langs}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \subfloat{{\includegraphics[scale=0.14]{images/Plutchik-wheel.png}}}%
    \label{adsad}
    \fixme{image not included in repo.}
    %\subfloat{{\includegraphics[scale= 0.79]{images/PLUTCHIKWHEEL.pdf}}}%
    \caption{Left: The Plutchik wheel of emotions: \url{https://en.wikipedia.org/wiki/Robert_Plutchik}.Right: The 10 different categories of emojis we have split our dataset into. 8 of them are from the Plutchik wheel of emotions, 1 contains other miscellanea emojis and the last contains only the mask emoji}%
    \label{fig:example}%
\end{figure}

@@

Due to the fact that emojis such as crying-face with tears, dominate the $\emoticon$ dataset (Table X),
we allow the model to predict up to 5 unique emojis for one tweet, to promote more diversity among our results.
This way, the results can be more meaningful. Further research, can include a more balanced $\emoticon$ dataset.
We collect the 5 predicted emojis, and after mapping them to the correct sentiment category, we calculate their 
percent out of the total number of emojis predicted for that day.
We show are results in Figure X.

\begin{figure}[ht]
    \centering
    \fixme{image not included in repo.}
    %\includegraphics[width=\textwidth]{images/corona_dataset_graph.pdf}
    \caption{The graph presents a bar plot of the number of tweets per day contained in the $\corona$ dataset;
    a line plot for the 8 different emotions from the Plutchik wheel: joy, anticipation,anger, and for the use of the mask emoji.
    We also include some of the important timelines of COVID-19:100 thousand,1 million,10 million cases alongside with some of the W.H.O responses}
    \label{fig:tweets_per_day_sent}
\end{figure}

\section{Related Work}
\label{sec:related}
\subsection{Datasets:}
It is now worth mentioning previous datasets related with sentiment and emotion classification. The Sentiment Evaluation task 2018 \cite{mohammad-etal-2018-semeval} presents a dataset of English, Arabic and Spanish tweets extracted from Twitter API, labelled for an array of subtasks on inferring the affectual state of a person from their tweet. Seventy-five teams submitted to one or more of the five total tasks; however, most of the submissions where for the language English. 
\cite{liu2019dens} introduces the DENS dataset, for multi-class emotion analysis. By collecting both English classic literature and modern online narratives, and by fine-tuning the pre-trained uncased BERT-large model to the multi-class passage classification task they achieved a micro-F1 average score of 60.4\%.
%\cite{liu2019dens}

%\cite{SemEval2018Task1}
\subsection{Pretrained models:}
On the domain of Pre-trained models for Natural Language Tasks, NVIDIA's researchers have published 
\cite{puri2018large} where by using Recurrent Neural Networks on a 40 GB Amazon Review dataset demonstrate 
the scalability and transfer of the RNNs. By utilizing mixed precision arithmetic and 
a 32k batch size distributed on 128 GPUs, they trained a character-level 4096-dimension mLSTM.
Furthermore, \cite{kant2018practical} claim that large-scale unsupervised language modeling combined 
with finetuning, provides a solution to the Multi-Emotion sentiment classification (Plutchik),
including those with label class imbalance and domain-specific context. By training an attention-based
transformer network on a Amazon 40 GB dataset, it outperforms the mLSTM model, while fine-tuning significantly 
improves performance for both Transformers and mLSTM.
%\cite{puri2018large}

%\cite{kant2018practical}

\subsection{Examples of large scale sentiment analysis:}
\cite{mohammad2017stance} explores both stance and sentiment analysis by providing a dataset of annotated tweet-target pairs, organized
a shared Task competition on Stance. Their stance detection system achieved an F-score of 70.3 \%, where they utilized an linear-kernel
SVM classifier. Their stance dataset contains 4k tweets, aimed towards topics such as Hillary Clinton, Atheism and etc. In addition,
\cite{yang2015twitter} provides an insight into measuring emotional contagion in Social Media. By using SentiStrengh (a sentiment analysis program),
and the findings of a study which claims that individuals are more likely to adopt positive or negative emotions if these are over-expressed in
their social network; the authors pursuit in establishing a relation between the sentiment of a tweet and that of the tweets that its author may have seen in a short
time period preceding its posting. Interestingly, they raise ethical concerns as they require massive-scale content manipulation with unknown consequences for the individuals therein involved.
Finally, the provide noteworthy limitations of observational experiments.
%\cite{mohammad2015sentiment}

%\cite{hemmatian2017survey}

%\cite{yang2015twitter}
\subsection{Emoji Prediction:}
It is now worth mentioning previous work on Emoji Prediction. \cite{barbieri-etal-2018-semeval} offered 2 subtasks for multilingual-emoji prediction: English and Spanish. By using Twitter API,
they located tweets either in the US (600k total) or in Spain (120k total). The tweets only included the one's with a single emoji and where limited to the top 20 emojis used across those countries. \cite{Tubingen_Olso} achieved 
the best performance in both the English and Spanish Tweets: F1-Score: 35.99 \%, F1-Score: 22.36 \% respectively obtained by an SVM classifier with bag-of-n-grams features. One of the best performing teams 
\cite{baziotis-etal-2018-ntua-slp}, achieved an F1-score of 35.36 \% on the English tweets, by using LSTM architecture with attention mechanism, initializing the embedding layer with word2vec and training end-to-end with back-propagation. 
The preprocessing tool they used was ekprahsis \cite{baziotis-etal-2017-datastories-semeval} which contains social tokenizer aimed for social media, spell correction and word segmentation which can be used for hashtag segmentation. Finally, \cite{towards_understanding_creatieve_lang}
explores both Irony Detection and the Emoji Prediction Task. They highlight that the knowledge the models gain is entirely from the corresponding training data, such training mechanism may work well for traditional text genres with formal sentences; however; 
it usually achieves an unsatisfiable performance with informal text, such as social media text.  By adopting a transfer learning model based on pretrained-BERT they achieved an F1-Score of 38.52 \% on the Emoji Prediction task. Issues raised by the authors were: overfitting 
due to the lack of more training data to fine-tune the system and time complexity.  
\section{Discussion}
\label{sec:discussion}

>>>>

\begin{figure}%
    \centering
    \subfloat{{\includegraphics[scale=0.24]{images/dis_country.eps}}}%
    \label{adsad}
    \subfloat{{\includegraphics[scale =0.24]{images/dis_lang.eps} }}%
    \caption{2 Figures side by side}%
    \label{fig:example}%
\end{figure}

@@

@@

@@

Importantly, duplicate tweets are included in the $\corona$ dataset,
but they are not included in the $\emoticon$ dataset.
This is because of the purpose of the $\emoticon$ dataset. 
We aimed to apply our $\model$ to this dataset,
which is something with free user input where our training data is not fully representative of the eventual data our model will be applied to.
Therefore this limits our abilities to make assumptions and could possibly inflate our sense of model efficacy.
On the other hand when dealing with the $\corona$ dataset,
duplicate inputs result in some distribution on our outputs.
Since we want to map out the public's emotional response to the coronavirus, it is important 
for those distributions to be maintained.

@@

\subsection{Training procedure and performance on $\emoticon$}
To generate $\model$, we utilized the pre-trained BERT model \cite{bert} by fine-tuning it to our multilingual emoji prediction task. 
BERT is a new language representation model, which is aimed in pretraining deep bidirectional representations from unlabeled text by jointly conditioning on both left and right context in all layers.
Therefore, the pre-trained model can be easily fine-tuned by adding another output layer.
One of the reasons why we picked BERT is due to its performance on the General Language Understanding Evaluation (GLUE) \cite{} benchmark.
It is comprised of nine language understanding tasks, assembled from a diverse dataset which includes insight into model performance with respect to a wide range of linguistic phenomena.
At the time of writing, BERT and its variations hold a number of top achieving scores in the GLUE leader-board \ref{leaderboard}.

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{images/F1_LANG_EMOJIS.pdf}
    \caption{F1-score performance on the top 15 performing emojis out of the 80 emojis trained. 
    \textbf{BERTmoji L.L} is the model where the last layer is trained. \textbf{BERTmoji} is the fully trained model.}
    \label{fig:tweets_per_day}
\end{figure}

@@

@@

\begin{figure}[!ht]
    \centering
    \includegraphics[width=\textwidth]{images/PREDICTMOJI.pdf}
    \caption{The table first column presents the top 10 languages of our $\emoticon$; 
    the second column includes the sliding window interpretations of the translations from the original English sentence performed with Google Translate;
    the third column shows the resulting top 5 emojis \textbf{BERTmoji} generated.
     }
    \label{fig:prediction_top10_langs}
\end{figure}

We now precede in testing \textbf{BERTmoji} ability to predict emojis for different languages.
We decided on picking an English sentence that expressed emotions and could possibly appear in twitter,
we then translated from English to the other nine languages from Figure 2 using Google Translate.
The sentence was: "Thinking about all the things I didn't do today, ok bed time ... \#tired \#sleep."
In addition, we also applied the sliding window algorithm to the translated sentences,
in order to observe which words were more significant for the \textbf{BERTmoji} across the translations.
The results are shown in Figure 6.

\begin{figure}[!ht]
    \centering
    \subfloat{{\includegraphics[scale=0.14]{images/Plutchik-wheel.png}}}%
    \label{fig:plu_wheel}
    \subfloat{{\includegraphics[scale= 0.79]{images/PLUTCHIKWHEEL.pdf}}}%
    \caption{Left: The Plutchik wheel of emotions: \url{https://en.wikipedia.org/wiki/Robert_Plutchik}.Right: The 10 different categories of emojis we have split our dataset into. 8 of them are from the Plutchik wheel of emotions, 1 contains other miscellanea emojis and the last contains only the mask emoji}%
    \label{fig:Mapped_emojis}%
\end{figure}

@@

\begin{figure}[!ht]
    \centering
    \includegraphics[width=\textwidth]{images/corona_dataset_graph.pdf}
    \caption{The graph presents a bar plot of the number of tweets per day contained in the $\corona$ dataset;
    a line plot for the 8 different emotions from the Plutchik wheel: joy, anticipation,anger, and for the use of the mask emoji.
    We also include some of the important timelines of COVID-19:100 thousand,1 million,10 million cases alongside with some of the W.H.O responses}
    \label{fig:tweets_per_day_sent}
\end{figure}

\begin{figure}[!ht]
    \centering
    \includegraphics[width=\textwidth]{images/true_pred_rotated.pdf}
    \caption{The true stacked bar presents the actual Plutchik wheel's mapped responses from the $\corona$ dataset while the predicted stacked bar graph presents the predicted emoji responses mapped to the Plutchik wheel following Figure  \ref{fig:Mapped_emojis} }
    \label{fig:actual vs pred}
\end{figure}

@@

Due to the fact that emojis such as crying-face with tears, dominate the $\emoticon$ dataset,
we allow the model to predict up to 5 unique emojis for one tweet, to promote more diversity among our results.
This way, the results can be more meaningful. Further research, can include a more balanced $\emoticon$ dataset.
We collect the 5 predicted emojis, and after mapping them to the correct sentiment category, we calculate their 
percent out of the total number of emojis predicted for that day. 
In order to understand the results we collected all the emojis from the tweets in the $\corona$ and mapped them to the categories in Figure \ref{fig:Mapped_emojis}.

\section{Related Work}
\label{sec:related}
\subsection{Datasets:}
It is now worth mentioning previous datasets related with sentiment and emotion classification. The Sentiment Evaluation task 2018 \cite{mohammad-etal-2018-semeval} presents a dataset of English, Arabic and Spanish tweets extracted from Twitter API, labelled for an array of subtasks on inferring the affectual state of a person from their tweet. Seventy-five teams submitted to one or more of the five total tasks; however, most of the submissions where for the language English. 
\cite{liu2019dens} introduces the DENS dataset, for multi-class emotion analysis. By collecting both English classic literature and modern online narratives, and by fine-tuning the pre-trained uncased BERT-large model to the multi-class passage classification task they achieved a micro-F1 average score of 60.4\%.

\subsection{Pretrained models:}
On the domain of Pre-trained models for Natural Language Tasks, NVIDIA's researchers have published 
\cite{puri2018large} where by using Recurrent Neural Networks on a 40 GB Amazon Review dataset demonstrate 
the scalability and transfer of the RNNs. By utilizing mixed precision arithmetic and 
a 32k batch size distributed on 128 GPUs, they trained a character-level 4096-dimension mLSTM.
Furthermore, \cite{kant2018practical} claim that large-scale unsupervised language modeling combined 
with finetuning, provides a solution to the Multi-Emotion sentiment classification (Plutchik),
including those with label class imbalance and domain-specific context. By training an attention-based
transformer network on a Amazon 40 GB dataset, it outperforms the mLSTM model, while fine-tuning significantly 
improves performance for both Transformers and mLSTM.

\subsection{Examples of large scale sentiment analysis:}
\cite{mohammad2017stance} explores both stance and sentiment analysis by providing a dataset of annotated tweet-target pairs, organized
a shared Task competition on Stance. Their stance detection system achieved an F-score of 70.3 \%, where they utilized an linear-kernel
SVM classifier. Their stance dataset contains 4k tweets, aimed towards topics such as Hillary Clinton, Atheism and etc. In addition,
\cite{yang2015twitter} provides an insight into measuring emotional contagion in Social Media. By using SentiStrengh (a sentiment analysis program),
and the findings of a study which claims that individuals are more likely to adopt positive or negative emotions if these are over-expressed in
their social network; the authors pursuit in establishing a relation between the sentiment of a tweet and that of the tweets that its author may have seen in a short
time period preceding its posting. Interestingly, they raise ethical concerns as they require massive-scale content manipulation with unknown consequences for the individuals therein involved.
Finally, the provide noteworthy limitations of observational experiments.

\subsection{Emoji Prediction:}
It is now worth mentioning previous work on Emoji Prediction. \cite{barbieri-etal-2018-semeval} offered 2 subtasks for multilingual-emoji prediction: English and Spanish. By using Twitter API,
they located tweets either in the US (600k total) or in Spain (120k total). The tweets only included the one's with a single emoji and where limited to the top 20 emojis used across those countries. \cite{Tubingen_Olso} achieved 
the best performance in both the English and Spanish Tweets: F1-Score: 35.99 \%, F1-Score: 22.36 \% respectively obtained by an SVM classifier with bag-of-n-grams features. One of the best performing teams 
\cite{baziotis-etal-2018-ntua-slp}, achieved an F1-score of 35.36 \% on the English tweets, by using LSTM architecture with attention mechanism, initializing the embedding layer with word2vec and training end-to-end with back-propagation. 
The preprocessing tool they used was ekprahsis \cite{baziotis-etal-2017-datastories-semeval} which contains social tokenizer aimed for social media, spell correction and word segmentation which can be used for hashtag segmentation. Finally, \cite{towards_understanding_creatieve_lang}
explores both Irony Detection and the Emoji Prediction Task. They highlight that the knowledge the models gain is entirely from the corresponding training data, such training mechanism may work well for traditional text genres with formal sentences; however; 
it usually achieves an unsatisfiable performance with informal text, such as social media text.  By adopting a transfer learning model based on pretrained-BERT they achieved an F1-Score of 38.52 \% on the Emoji Prediction task. Issues raised by the authors were: overfitting 
due to the lack of more training data to fine-tune the system and time complexity.  
\section{Discussion}
\label{sec:discussion}
